Interisland movements and oceanic swimming of woodland caribou in Newfoundland

### 2020-03-18 paper/manuscript.Rmd
Update manuscript.Rmd and manuscript.md

<!-- add numbers in here -->
In total, these XX swimming events occurred throughout the ice-free season, with
a peak in November. On average, caribou swam between islands approximately ever
XX days, but some individuals swam up to XX times per year (range XX-XX).
Caribou may swim between islands in the ocean for similar reasons they swim in
freshwater [@Leblond2016]. We propose that one such explanation, the forage
limitation hypothesis, is likely driving oceanic swimming events [@Miller2002].
<!--Is it better
to just state our results here, or give this sort of teaser? Initially I had "86
events by 3 individuals" here, but then we ignore that for a couple paragraphs
of context before getting back into it... which seemed weird
QW: I agree. I've added some Fogo context-->

>>>>

<!-- add numbers in here -->
In total, these XX swimming events occurred throughout the ice-free season, with
a peak in November. On average, caribou swam between islands approximately ever
XX days, but some individuals swam up to XX times per year (range XX-XX).
Caribou may swim between islands in the ocean for similar reasons they swim in
freshwater [@Leblond2016]. We propose that one such explanation, the forage
limitation hypothesis, is a likely explanation for oceanic swimming for caribou that live on islands in the Fogo Island archipelago.
<!--Is it better
to just state our results here, or give this sort of teaser? Initially I had "86
events by 3 individuals" here, but then we ignore that for a couple paragraphs
of context before getting back into it... which seemed weird
QW: I agree. I've added some Fogo context-->
